|

### 2022-06-14 draft-1.Rmd
Fix (?) `officedown` table numbering

```{r extent, fig.width = 4.5, fig.cap = "Extent of ZIP codes (dark gray) within Western NC (light gray)"}
knitr::include_graphics("fig/brownExtent.png")
```

@@

```{r gs-extent, fig.width = 4.5, fig.cap = "Extent of combined PAD-US and ParkServe greenspace areas (dark gray)"}
knitr::include_graphics("fig/brownGSExtent.png", dpi = 600)
```

@@

```{r moran-table}
moran <- read_rds("data/moran.Rds") %>%
  mutate(across(.fns = as.character))

knitr::kable(moran,
             format = "latex",
             col.names = c("Variable", "Moran's I", "Expected", "Variance", "SD", "p value"),
             caption = "Calculated statistics for Moran’s I across predictor and response variables")

@@

```{r vif}
basic_list <- read_rds("data/basic_list.Rds")
basic_list %>% map_dfr(regclass::VIF) %>% t() %>% `row.names<-`(c("Mean NDVI", "Greenspace Area", "Percent White", "Income", "Amenities", "Trails")) %>% `colnames<-`(c("MHLTH", "DEPRESSION", "SLEEP")) %>% 
  knitr::kable(digits = 4, caption = "Variance Inflation Factors for variables")

@@

```{r, lagrange}
l$p.value <- as.character(signif(l$p.value))
knitr::kable(l, caption = "Results from Robust Lagrange Multiplier Test. Spatial lag regression was used in this analysis")
```

@@

```{r lisa, fig.width=4.5, fig.cap = "Results from LISA highlighting general trend from hot (high-high) to cold(low-low) clustering of each variable. Note that not all locations have a p-value < 0.05 and that this figure is meant as a visual aid"}
knitr::include_graphics("fig/brownLISA.png")
```

@@

Spatial regression analysis found that none of the greenspace metrics were associated with reductions in reported poor mental health (Table \@ref(tab:sarlm-table)). Percent of the ZIP Code that is White ($\beta = -4.476, p >0.001$) and percent of households in the ZIP Code making over \$125,000 ($\beta = -4.638, p > 0.001$) were significantly associated with reductions in mental health outcomes (Table \@ref(tab:sarlm-table)).

```{r sarlm-table}
model_list %>%
  map(function(x) {
    extract.Sarlm2(x)
  }) %>%
  texreg::texreg(
    single.row = T,
    booktabs = T,
    dcolumn = T,
    custom.model.names = c("MHLTH", "DEPRESSION", "SLEEP"),
    custom.coef.names = c(
      NA,
      "Mean NDVI",
      "Greenspace Area",
      "Percent White",
      "Income",
      "Amenities",
      "Trails",
      "rho"

    ),
    float.pos = "h", caption = "Spatial lag regression coefficients for each mental health outcome"
  )
```

@@

Greenspace metrics are not significantly associated with depression (Table \@ref(tab:sarlm-table)). Percent of the ZIP Code that is White was also not associated with changes in depression diagnoses. Percent of households making over \$125,000 per year was significantly associated with reductions in depression diagnoses ($\beta = -2.924, p = 0.004$) (Table \@ref(tab:sarlm-table)).

@@

Spatial regression found poor sleep to be significantly associated with greenspace metrics (Table \@ref(tab:sarlm-table)). Greenspace quantity ($\beta = 0.743, p = 0.026$) was significantly associated with an increase in reported poor sleep, while greenspace amenities ($\beta = -0.015, p < 0.001$) were significant;y associated with a decrease in reported poor sleep. Percent White ($\beta = -6.980, p < 0.001$) and percent of households making over \$125,000 ($\beta = -5.707, p > 0.001$) were both significantly associated with reductions in reported poor sleep outcomes (Table \@ref(tab:sarlm-table)).

>>>>

```{r extent, fig.width = 4.5, fig.height=1.72, fig.id = "extent", fig.cap = "Extent of ZIP codes (dark gray) within Western NC (light gray)"}
knitr::include_graphics("fig/brownExtent.png")
```

@@

```{r gs-extent, fig.width = 4.5, fig.height=2.26, fig.id = "gs-extent", fig.cap = "Extent of combined PAD-US and ParkServe greenspace areas (dark gray)"}
knitr::include_graphics("fig/brownGSExtent.png")
```

@@

```{r moran-table, tab.id = "moran-table", tab.cap = "Calculated statistics for Moran’s I across predictor and response variables"}
moran <- read_rds("data/moran.Rds") %>%
  mutate(across(.cols = -1, .fns = function(x){signif(x, 3) %>% as.character()})) %>% 
`colnames<-`(c("Variable", "Moran's I", "Expected", "Variance", "SD", "p value"))

moran
# knitr::kable(moran,
#              format = "latex",
#              col.names = c("Variable", "Moran's I", "Expected", "Variance", "SD", "p value"))

@@

```{r vif, tab.id = "vif", tab.cap = "Variance Inflation Factors for variables"}
basic_list <- read_rds("data/basic_list.Rds")
bl <-
  basic_list %>% map_dfr(regclass::VIF) %>% t() %>% `row.names<-`(c(
    "Mean NDVI",
    "Greenspace Area",
    "Percent White",
    "Income",
    "Amenities",
    "Trails"
  )) %>% 
  `colnames<-`(c("MHLTH", "DEPRESSION", "SLEEP")) %>% 
  as.data.frame() %>% 
  tibble::rownames_to_column("Variable") %>% 
  mutate(across(2:4, .fns = signif, digits = 4))
bl

@@

```{r, lagrange, tab.id = "lagrange", tab.cap = "Results from Robust Lagrange Multiplier Test. Spatial lag regression was used in this analysis"}
# l$p.value <- as.character(signif(l$p.value))
l2 <- l[1:4, -3] %>%
  mutate(across(2:3, signif, digits = 4)) %>%
  mutate(Method = c("Spatial Error (SE)",
                    "Spatial Lag (SL)",
                    "Robust SE",
                    "Robust SL")) %>% 
  `colnames<-`(c("Method", "Lagrange Multiplier", "p-value"))

l2

@@

```{r lisa, fig.width=4.5, fig.id = "lisa", fig.cap = "Results from LISA highlighting general trend from hot (high-high) to cold(low-low) clustering of each variable. Note that not all locations have a p-value < 0.05 and that this figure is meant as a visual aid"}
knitr::include_graphics("fig/brownLISA.png")
```

@@

Spatial regression analysis found that none of the greenspace metrics were associated with reductions in reported poor mental health (Table \@ref(tab:sarlm)). Percent of the ZIP Code that is White ($\beta = -4.476, p >0.001$) and percent of households in the ZIP Code making over \$125,000 ($\beta = -4.638, p > 0.001$) were significantly associated with reductions in mental health outcomes (Table \@ref(tab:sarlm)).

```{r tab.id = "sarlm", tab.cap = "Spatial lag regression coefficients for each mental health outcome"}
model_list %>%
  map(function(x) {
    extract.Sarlm2(x)
  }) %>%
  texreg::matrixreg(
    single.row = T,
    booktabs = T,
    dcolumn = T,
    custom.model.names = c("MHLTH", "DEPRESSION", "SLEEP"),
    custom.coef.names = c(
      NA,
      "Mean NDVI",
      "Greenspace Area",
      "Percent White",
      "Income",
      "Amenities",
      "Trails",
      "rho"

    ),
    float.pos = "h"
  ) %>% 
  as_tibble() %>% 
  `colnames<-`(.[1, ]) %>% 
  .[-1, ]
```

@@

Greenspace metrics are not significantly associated with depression (Table \@ref(tab:sarlm)). Percent of the ZIP Code that is White was also not associated with changes in depression diagnoses. Percent of households making over \$125,000 per year was significantly associated with reductions in depression diagnoses ($\beta = -2.924, p = 0.004$) (Table \@ref(tab:sarlm)).

@@

Spatial regression found poor sleep to be significantly associated with greenspace metrics (Table \@ref(tab:sarlm)). Greenspace quantity ($\beta = 0.743, p = 0.026$) was significantly associated with an increase in reported poor sleep, while greenspace amenities ($\beta = -0.015, p < 0.001$) were significant;y associated with a decrease in reported poor sleep. Percent White ($\beta = -6.980, p < 0.001$) and percent of households making over \$125,000 ($\beta = -5.707, p > 0.001$) were both significantly associated with reductions in reported poor sleep outcomes (Table \@ref(tab:sarlm)).
